
\documentclass[12pt,a4paper]{article}

%\pdfoutput=1

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{mathabx}
\usepackage{lmodern}
\usepackage{listings}
\usepackage{units}
\usepackage{siunitx}
\usepackage{icomma}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{color}
\usepackage{pgf}
\DeclareMathOperator{\acosh}{arccosh}
\newcommand{\N}{\ensuremath{\mathbbm{N}}}
\newcommand{\Z}{\ensuremath{\mathbbm{Z}}}
\newcommand{\Q}{\ensuremath{\mathbbm{Q}}}
\newcommand{\R}{\ensuremath{\mathbbm{R}}}
\newcommand{\C}{\ensuremath{\mathbbm{C}}}
\newcommand{\rd}{\ensuremath{\mathrm{d}}}
\newcommand{\id}{\ensuremath{\,\rd}}
\usepackage{hyperref}
%\usepackage{a4wide} % puts the page numbering further down the page.
\usepackage{pdfpages}
\usepackage{epstopdf}
\DeclareGraphicsExtensions{.eps}
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

\title{Ethics interview}
\author{Marcus Malmquist, marmalm}
\date{\today}

\begin{document}
\maketitle

\section{Interview}
Name: Per\\
Work: ABB AB\\
Proffession: Sales manager\\

\noindent- Have you come across any situation as a professional when you needed to think through ethical aspects before making a decision? Tell me a bit more, please!
\begin{quote}
  ``Once when I gave an quotation to a company, ****, it was handed over to one of our competitor. I reported this to my superior. This was a kind of a business ethics problem.''
\end{quote}

\noindent- What principles guided your decision?
\begin{quote}
  ``An quotation is targeted at a specific customer and is not allowed to be handed to anyone else according to business-related ethical aggreements (code of conduct).''
\end{quote}

\noindent- What did you decide?
\begin{quote}
  ``I reported this to my superior.''
\end{quote}

\noindent- Were you at ease with this?
\begin{quote}
  ``Yes.''
\end{quote}

\noindent- Was there a dilemma involved?
\begin{quote}
  ``It disturbed my bussiness relation and trust with company ****. It gives the competitors an unfair advantage.''
\end{quote}

\noindent- Have you heard of other situations, from colleagues, news etc. where you might expect to need ethics-related thinking for professional decision-making?
\begin{quote}
  ``A few years ago I heard about a cartel setting the price of components on the market. We work in accordance with our code of conduct, which limits these issues. Situations involving questionable ethics typically happens behind closed doors.''
\end{quote}

\noindent- Did you get any formal training in ethics for your profession?
\begin{quote}
  ``Yes, training code of conduct.''
\end{quote}

\noindent- Has it helped, or would it have helped?
\begin{quote}
  ``Yes, it has helped me.''
\end{quote}

\noindent- Would you like to choose the three most important principles or guidelines for this type of decisionmaking in your profession? What is useful, and what is not? Think of your own situation if you want a context.
\begin{quote}
  \begin{itemize}
  \item ``Never offer or accept bribes''
  \item ``Know what information you are allowed to use in your work, e.g. are you allowed to use knowlege about the price your competitors sell their products when setting the price of your products.''
  \item ``Work actively with safety.''
  \end{itemize}
\end{quote}

\noindent- Is it OK with you if I use your name or would you prefer to be anonymous for my course assignment?
\begin{quote}
  ``It is OK.''
\end{quote}
\end{document}