\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\title{Peer review: 3D projection by Lukas Mared}
\author{Marcus Malmquist}
\date{\today}

\begin{document}
\maketitle
\section{General}
Overall it was a good report and you explained thoroughly what you did. Most of my comments are about the structure of the report which perhaps is mostly down to personal preference. A note on the images used is that i think you need to include the license it is distributer under if it was not made by you, but this may not be a concern since the report won't be published.

\section{Background}
Looks good but the title and the background should perhaps give more information as to what will be presented in the report. This could also be included in some kind of abstracd.

\section{Theory}
Goes into detail about how the optical components work and gives a good understanding of how images can be isolated utilizing the polarization of light.
When explaining polaization, erhaps introduce light as a linear combination in some reference plane (e.g. $x$- and $y$-axis) and talk about it as a phase-shift between the two components. This would make it easier to understand (at least for me).

The paragraph where Figure~3 is introduced may seem a bit confusing when talking about linearly polarized light turning into circular and then back to linear while the image shows circular polirized light turning into circular and then back to circular. It might be better to find/make an image showing what you talked about.

\section{The Laboration}
The introduction to this section should probably be moved to section~1.
\subsection{Equipment}
Perhaps include some schematic image of how the components were set up. This section and section~3.2.3 could be put in a section of their own before section~3.

\subsection{Investegation}
Since the bullet lists only describes the subesctions it don't need to be included, and the subsections could also be changed to a statement rather than a question, since you are presenting what you already have done.

It was good that you checked how the components were constructed. Did you have any relevant hypothesis that could be added in a section before section~3. 

\section{Discussion}
Good observations. Did you have any hypothesis about how the setup should be and if it worked the way you thought? Would be interesting to read abous since the overhead could potentially change things. Also maybe discuss something about if you managed to allign the 3D glasses perfectly which is more likely a source of error rather than how the glasses themselves were constructed (since you usually don't see any ghost images in 3D-cinemas).

\end{document}
